% ! Tex program = xelatex
\documentclass{article}
\usepackage{pst-node}
% 中文
% \usepackage[UTF8]{ctex}

% For more choices
% \input{/Users/anye_zhenhaoyu/Desktop/preamble.tex}
% \input{/Users/anye_zhenhaoyu/Desktop/ln_preamble.tex}

% \input{/path/preamble.tex}
% \input{/path/ln_preamble.tex}

% On my MAC's Desktop
\input{../preamble}

\graphicspath{{figures/}}

\begin{document}
% \tableofcontents
\title{Homework 2}
\maketitle
\section*{Problem 1}
Let $T(n)$ be the numebr of all the bit operation we have done after  $n$ ADDs, e.g., $T(1)=1,\,T(2)=3$. $C_n\defeq T(n)-T(n-1)$ and $S_k\defeq T(2^k-1)$.
NB: $(2^k-1)_2=\underbrace{11\cdots1}_k$.

Then we have
\[
	S_k=C_{2^{k-1}}+2S_{k-1}=k+2S_{k-1}
\] which entails
\[
	T(2^k-1)=S_k=2^{k+1}-k-2\qand T(2^k)=2^k-1
	.\]
Thus $\forall n\in\set{2^{k-1},\cdots,2^{k}-1}$
\[
	C(1)+C(2)+\cdots+C(n)=T(n)<T(2^k)<4n\Longrightarrow \mathrm{LHS}=n\+O(1)
	.\]
Finally, the amortized cost of ADD is $\+O(1)$.

\section*{Problem 2}
\textbf{(a).}
The counter-example:
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\node (1) at(0,0) {1};
		\node (2) at(1,1) {2};
		\node (3) at(2,0) {3};
		\draw[->] (1)--(2);
		\draw[->] (2)--(3);
		\draw[->] (1)--(3);
		\node (-1) at(0.2,0.7) {-1};
		\node (-2) at(1,0.3) {-2};
		\node (-3) at(1.7,0.7) {-2};
	\end{tikzpicture}
\end{figure}
The shortest path from 1 to 3 should be:$1\to2\to3$. While this algorithm will return $1\to3$ directly by $(C-2)<(C-1)+(C-2)$ where $C>2$ is the number added to each edge.
\\\\
\textbf{(b).} Worked.

Trivially, $\forall$ path $p$ form $s$ to $v_l$, $p=(s,v_1,v_2,\cdots,v_l)$ where $v_i$ belongs to layer $i$.

Let $p_0=\argmin_p(p \text{ is the shortest path from $s$ to $v_l$})$. Then
\[
	p_0=\argmin_p\qty(l\times C+\sum_{\text{weight $w$ in }p} w)=\argmin_p\qty(\sum_{\text{weight $w$ in }p} w)
\]
where RHS is what we want.

\section*{Problem 3}
\textbf{(a).}
I was inspired by the \textcolor{blue}{Hint} from Chihao Zhang. Let $s$ be the beginning vertex. The algorithm is as follows.

\begin{enumerate}
	\item Construct a graph $H$ having the same topology of  $G$. In $H$, weight $w=rc_{uv}-p_v$ w.r.t. edge $(u,v)$.
	\item Determine if there is a negative loop that $s$ could reach (implement SPFA or Bellman-Ford).
	\item If 2. returns true, then $\exists C$: $\sum_{(u,v)\in C}rc_{uv}-p_v<0$ which means that $r<r^*$. Otherwise $r\ge r^*$.
\end{enumerate}
The complexity is $\+O(\abs{V}\abs{E})$.
\\\\
\textbf{(b).}
For simplicy, ALG.a denotes the algorithm demonstrated in (a).

\begin{algorithm}[H]
	\caption{Find the cycle which has a good profit-to-cost ratio in the given graph}
	\label{fc}
	\begin{algorithmic}
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE A graph $G$
		\ENSURE A good enough cycle $C$.
		\STATE $left\gets 0$, $right\gets R$.
		\WHILE{$right-left>\varepsilon$}
		\STATE $r\gets\flatfrac{(right+left)}{2}$ 
		\STATE Implement ALG.a with the input: ratio $r$ and graph  $G$
		\IF{$r>r^*$}
		\STATE $left\gets r$
		\ELSE
			\STATE $right\gets r$
		\ENDIF
		\ENDWHILE
		\STATE Construct the graph $H$ following the rules shown in (a). step 1 with $r=left$
		\IF{$H$ dose not has a negative loop (Under this case, $left = r^*$.)}
		\STATE We could reconstruct the graph  $H$ with $r=left-\flatfrac{\varepsilon}{2}$
		\ENDIF
		\STATE Find a negative loop $C$ in $H$ contained $s$ by Bellman-Ford (More details are in Appendix ALG.\ref{fn})
		\RETURN $C$
	\end{algorithmic} 
\end{algorithm}
Soundness of ALG.\ref{fc}: Obviously, $\forall left,\,right:$ $left\le r^*\le right$. When the ``while'' operation ends, we have $r^*-\varepsilon\le left\le r^*$.
Thus
\[
	\sum_{(u,v)\in C}\qty(left\times c_{uv}-p_v)\le 0
	\Longrightarrow
	r^*-\varepsilon\le left\le r(C)
.\]
The complexity of ALG.\ref{fc}: 
\[
	T(\abs{V},\varepsilon,R)
	=
	\+O\qty[\abs{V}\abs{E}\log_2\qty(\frac{R}{\varepsilon})]
	=
	\+O\qty[\abs{V}^3\log\qty(\frac{R}{\varepsilon})]
.\] 
\newpage
\section*{Problem 4}
\textbf{(a).} Trivially, G only has 2 vertices. $G$: $1--2$ and $G'$:  $1\longrightarrow 2$
\\\\
\textbf{(b).}
% First we define $A_{u}=\set{u}\cup\set{u\text{'s ancestor in $G'$}}$ and $D_{u}=\set{u}\cup\set{u\text{'s descendant in $G'$}}$. Also $G=(V_G,E_G)$ and  $G'=(V_{G'},E_{G'})$.
In $G$, we want to generate 2 paths $p_1$ and $p_2$ such that they share no edge, i.e., $\forall (u_1,v_1)$ in $p_1$ and $(u_2,v_2)$ in $p_2$, $(u_1,v_1)\ne (u_2,v_2)$. We do it by following steps:
\begin{enumerate}
	\item 
		In $G'$, there exist 2 paths $p_1$: $u\to v$ and $p_2$: $v\to u$.
	\item
		If $p_1$, $p_2$ have the same edge $(u',v')$, go to step.3.
	\item
		Assume that $p_1=(u\Rightarrow u'\to \Rnode{tov}{\underline{v'\Rightarrow v}})$ and $p_2=(\Rnode{vu}{\underline{v\Rightarrow u'}}\to v'\Rightarrow u)$ where $a\to b$ implies $a,b$ are adjacent and $a\Rightarrow b$ represents a path from a to b.
	\item Then update:
		$p_1=(u\Rightarrow \Rnode{uv}{\underline{u'\Rightarrow v}})$ and 
		$p_2=(\Rnode{vto}{\underline{v\Rightarrow v'}}\Rightarrow u)$.
		Here $u'\Rightarrow v$ is the inverse of $v\Rightarrow u'$ and $v\Rightarrow v'$ is the inverse of  $v'\Rightarrow v$.
	\item Repeat step 2 until $p_1$ and $p_2$ share no edge.
\end{enumerate}
\ncarc[arrows = ->, linecolor =blue, arcangle = -10, nodesep = 1pt]{vu}{uv}
\ncarc[arrows = ->, linecolor =red, arcangle = -20, nodesep = 1pt]{tov}{vto}
Trivially, $p_1$ and $p_2$ is what we want. Thus, forall $u,v$ in $V$, there are 2 paths from $u$ to $v$ and they share no edge in $G$ $\implies$ removing any single edge from $G$ will still give a connected graph.
\\\\
\textbf{(c).}
From a root $r$ we get a tree $T$ generated by DFS.
\begin{lemma}
	\label{ct}
	Suppose that a vertex $u$ has several subtrees $T_1,T_2,\cdots,T_k$. And we define: $T_i$ is strongly connected in $G$ if $\forall u,v\in$, $u$ could reach $v$ and $v$ could reach $u$ in $G$. Then:
	\[
		\forall i,\,T_i\text{ is strongly connected in }G
		\implies
		T_u\text{ is strongly connected in }G
	\] where $T_u$ is the $G$'s subtree with root $u$.
\end{lemma}
\begin{proof}
	We only need to prove $\forall i$, $\exists$ vertex $v$ in $T_i$, $(v,u')$ is a back edge in $E$ where $u'$ is the ancestor of $u$ or  $u=u'$.
	If not, assume $T_j$ does not satisfy this property. Then we cut the edge ``$e$'' from u to $T_j$.
	Noe we use the property of tree generated by DFS: ``if $(v_1,u_1)\in E$ where $v_1$ is in $T_j$ and $u_1$ is not in, then $u_1$ is the ancestor of $T_j$.''
	Now we have there is no edge from $T_j$ to $u$. Contradiction.
\end{proof}
Here we use induction:

every leaf is strongly connected in $G$. Then by lemma.\ref{ct}, the whole ``tree'' is connected in $G$, which means $G'$ is strongly connected.
\\\\
\textbf{(d).}
Assume that $G$ is connected (or it is trivial).
we design the algorithm intuitively,
\begin{enumerate}
	\item $n\gets 0$
	\item Generate $G'$ through the given rule. (Easy to implement)
	\item Analyse $G'$ using algorithm in ``Slide-06 Page $\S127$ Super Plan'' to find all SCCs 
	\item For every $(u,v)\in E_{G'}$, if $u,v$ belong to different SCCs, then $n\gets n+1$
\end{enumerate}
The correctness of this algorithm holds naturaly because SCCs in Step.2 is a tree which only has tree edges and back edges.

The complexity is $\+O(\abs{V}+\abs{E})$.

\section*{Problem 5}
Get the smallest number $n$ by the following steps:
\begin{enumerate}
	\item Find all the SCCs in $G$, regard every of them as a node and keep the edges between different SCCs. Then we get a DAG: $G'$. 
	\item Separate $G'$ into $k$ isolated component $C_1,C_2,\cdots,C_k$ such that there is no edges between different components and $C_i$ is weakly connected.
	\item $T_i\defeq\text{number of tail vertex in }C_i$ and $H_i\defeq\text{number of head vertex in }C_i$.
	\item $n=k-1+\sum_{i=1}^k\max(T_i,H_i)$.
\end{enumerate}
Reference: \href{https://stackoverflow.com/questions/12681785}{Question.12681785, StackOverflow}.

\section*{Problem 6}
About 15 hours. Difficulty 4. Talked with Yilin Sun and Wei Jiang.

\section*{Appendix}
	How to find a negative loop in graph $H$? Here's the algorithm:
	\begin{algorithm}[H]
	\caption{Find the cycle which has a negative loop in the given graph}
	\label{fn}
	\begin{algorithmic}
		\STATE Implement Bellman-Ford algorithm, during which we record the parents for every updated vertex.
		\STATE In Bellman-Ford algorithm, vertex $v$ has been traversed for  $\abs{V}$ times. 
		\STATE Initiate an array: $\set{a_i}\gets 0$.
		\WHILE{$\forall i$, $a_i\le 1$}
		\STATE $a_v\gets a_v+1$
		\STATE $v\gets v\text{'s parent}$
		\ENDWHILE
		\STATE Suppose that $a_t=2$
		\RETURN $(t,\, t\text{'s parent},\,\cdots,\,t)$
	\end{algorithmic} 
\end{algorithm}
\end{document}
